Probabilistic Forecast Reconciliation

### 2018-08-08 Presentation/ProbForeRec.tex
updated presentation

  when $g(.)$ is linear it is easier to write $\tilde{\bm y}={\bm S}{\bm G}{\bm y}$

@@

  The last equality does not hold for ${\bm G}$ in general.

@@

  	\item Ergo reconciliation reduces the error, not only in expectation, but always. 

@@

  	Let the unreconciled density be elliptical with location  $\hat{\bm{\mu}}$ and scale $\hat{\bm{\Sigma}}$ and let the true predictive density be elliptical with location  ${\bm{\mu}}$ and scale ${\bm{S}}{\bm{\Omega}}{\bm{S}}'$.

@@

  		The true predictive distribution can be recovered via linear reconciliation.  The optimal (but infeasible) mapping is $g(\breve{\bm y})={\bm G}_{opt}\breve{\bm y}+{\bm d}_{opt}$ where $\bm{G}_{opt}={\bm\Omega}^{1/2}{\hat{\bm{\Sigma}}}^{-1/2}$ and ${\bm d}_{opt}={\bm G}_{opt}\left({\bm \mu}-\hat{\bm \mu}\right)$.

@@

    This follows from the closure property of elliptical distributions under affine transformations and marginalisation.

@@

  \begin{frame}{Reconciled v Unreconciled}

@@

   		\item If you want to see tables with numbers see the paper.

@@

    \begin{frame}{The paper}
    		\item A paper will be available soon (end of July).
    		\item Google {\em EBS Monash Working Paper}.
    		\item Or email me :)

>>>>

  when $g(.)$ is linear it is easier to write $\tilde{\bm y}={\bm S}{\bm G}\hat{\bm y}$

@@

  The last equality does not hold for ${\bm G}$ in general but does hold when ${\bm S}{\bm G}$ is a projection.

@@

  	\item Ergo reconciliation reduces the error and not just in expectation. 

@@

  	Let the true predictive densities be elliptical.

@@

  		There exists a function $g(.)$ such that the true predictive distribution can be recovered by linear reconciliation as long as the unreconciled probabilistic forecast comes from the correct elliptical class.

@@

    This follows from the closure property of elliptical distributions under affine transformations and marginalisation.  Conditions are also derived for when this $g(.)$ is also a projection.

@@

  \begin{frame}{Coherent v Incoherent}

@@

@@
